Cybersecurity Is Too Important To Be Left To The Specialists

### 2019-01-27 ITiCSE2019.tex
More restructuring

%%%% Proceedings format for most of ACM conferences (with the exceptions listed below) and all ICPS volumes.
%\documentclass[sigconf]{acmart}
\documentclass[sigconf,anonymous]{acmart}
\usepackage{paralist}
%\usepackage{url}
%\usepackage{enumitem}
%\usepackage[hyphenbreaks]{breakurl}

@@

\textbf{3. Professional Bodies}
The BCS, The Chartered Institute for IT (BCS) and the Institution of Engineering and Technology (IET) both accredit programmes in the general area of Computer Science and the more specialist area of Cybersecurity discipline areas. The accreditation provided by these institutes are underpinned by international Initiatives such as the Washington Accord\footnote{\url{http://www.ieagreements.org/accords/washington/}.} and Seoul Accord\footnote{\url{https://www.seoulaccord.org/}.}. These memoranda support the internationalising of the curriculum and promote consistency and parity in Computer Science Education globally.   These professional bodies are also registered charities and hence have responsibilities for public good which extends beyond short term job market needs \cite{Stensaker2006}, \cite{Mutereko2017}. Both the IET and The BCS have a long history of expecting coverage environmental factors within the programmes they accredit. The BCS has for a number of years been expecting significant coverage of Legal, Ethical, Social and Professional Issues \cite{Brooke2018}. Clearly Cybersecurity has been and continues to be part of these expectations.

Internationally the expectations regarding both the breadth and depth of the expected Cybersecurity coverage has been the subject of much discussion, debate and analysis. In parallel to the work complete by the ACM \cite{ACM2013a}, in the UK considerable effort was taken to ensure Industry, Higher Education, Government and the related Professional Bodies collaborated on a set of guidelines which are to the benefit of the various stakeholders and wider society \cite{Irons2016}. In 2013, an initiative was set up by (ISC)2, CPHC (the representative body of Computer Science Departments) and the Cabinet Office to examine embedding Cybersecurity into undergraduate degrees in the UK. Three workshops in 2013 and 2014 attempted to define the principles of Cybersecurity education and proposed a framework for embedding these principles in UK Computing Science curricula. Attendees at the workshops included industry, professional bodies, UK government departments and more than 30 Universities that offer undergraduate Computing Science degrees.  The BCS agreed to adopt the outputs into their accreditation criteria. This was the first time that Cybersecurity has been explicitly referenced within accreditation criteria for computing and IT-related degrees. The fact that Cybersecurity is included as a  component of the BCS accreditation criteria, reflects the importance placed on Cybersecurity and the expectation that all computing graduates should have knowledge and skills in Cybersecurity as they move towards Chartered status.

>>>>

%%%% Proceedings format for most of ACM conferences (with the exceptions listed below) and all ICPS volumes.
%\documentclass[sigconf]{acmart}
\documentclass[sigconf,anonymous]{acmart}
\usepackage{paralist}
\usepackage{url}
%\usepackage{enumitem}
\usepackage[hyphenbreaks]{breakurl}
\usepackage[T1]{fontenc}
\usepackage{hyperref}

@@

\textbf{3. Professional Bodies}
The BCS, The Chartered Institute for IT (BCS) and the Institution of Engineering and Technology (IET) both accredit programmes in the general area of Computer Science and the more specialist area of Cybersecurity discipline areas. The accreditation provided by these institutes are underpinned by international Initiatives such as the Washington Accord\footnote{\url{http://www.ieagreements.org/accords/washington/}.} and Seoul Accord\footnote{\url{https://www.seoulaccord.org/}.}. These memoranda support the internationalising of the curriculum and promote consistency and parity in Computer Science Education globally.   These professional bodies are also registered charities and hence have responsibilities for public good which extends beyond short term job market needs \cite{Stensaker2006}, \cite{Mutereko2017}. Both the IET and The BCS have a long history of expecting coverage environmental factors within the programmes they accredit. The BCS has for a number of years been expecting significant coverage of Legal, Ethical, Social and Professional Issues \cite{Brooke2018}. Clearly Cybersecurity has been and continues to be part of these expectations. 
\subsection{Developing Expectations}
Internationally the expectations regarding both the breadth and depth of the expected Cybersecurity coverage has been the subject of much discussion, debate and analysis. In parallel to the work complete by the ACM \cite{ACM2013a}, in the UK considerable effort was taken to ensure Industry, Higher Education, Government and the related Professional Bodies collaborated on a set of guidelines which are to the benefit of the various stakeholders and wider society \cite{Irons2016}. In 2013, an initiative was set up by (ISC)2, CPHC (the representative body of Computer Science Departments) and the Cabinet Office to examine embedding Cybersecurity into undergraduate degrees in the UK. Three workshops in 2013 and 2014 attempted to define the principles of Cybersecurity education and proposed a framework for embedding these principles in UK Computing Science curricula. Attendees at the workshops included industry, professional bodies, UK government departments and more than 30 Universities that offer undergraduate Computing Science degrees.  The BCS agreed to adopt the outputs into their accreditation criteria. This was the first time that Cybersecurity has been explicitly referenced within accreditation criteria for computing and IT-related degrees. The fact that Cybersecurity is included as a  component of the BCS accreditation criteria, reflects the importance placed on Cybersecurity and the expectation that all computing graduates should have knowledge and skills in Cybersecurity as they move towards Chartered status.
